---
title: "Fun with Real Estate"
output:
  pdf_document: default
  html_document: default
---
## Data Driven Real Estate Analysis ##

This dataset gives us a chance to look into the data on what really influences the sale of a house !


```{r Libraries, message=FALSE, warning=FALSE, echo=FALSE}
library(data.table)
library(FeatureHashing)
library(Matrix)
library(stringi)
#library(xgboost)
library(stringr)
require(randomForest)
require(caret)
require(dplyr)
require(ggplot2)
library(pROC)
library(dummies)
library(Metrics)
library(kernlab)
library(mlbench)
library(car)
```

###Plan

* Assemble the data and explore it
* Clean variables, build what is needed
* Three Models: Linear, randomForest, and xgboost
* Choose the best model and make the prediction for entry


###Clean the Data

So, what do we have here?
```{r load, echo=FALSE}
train <- read.csv("C:\\train.csv", stringsAsFactors=FALSE)
test <- read.csv("C:\\test.csv", stringsAsFactors=FALSE)

names(train)



```

```{r}

str(train)

```

```{r}
names(train)%in% names(test)
```

```{r formatting_street2}
table(train$Street)

pavedInd=train$paved[train$Street == "Pave"] <- 1
pavedInd=train$paved[train$Street != "Pave"] <- 0
table (pavedInd)
```

```{r}
table(train$LotShape)
```

I think the best steps to start with would be reformatting some character variables that we can easily convert to numeric. What's the street type about?

Not exactly fancy, let's just make that paved or not. What about Lot Shape?



I assume these are something like variations on "irregular". So let's go with regular or not, and then we'll have this shape variable still if we want to go more granular later.
Taking up land contour as the next.
```{r formatting_shape}
train$regshape[train$LotShape == "Reg"] <- 1
train$regshape[train$LotShape != "Reg"] <- 0
train$IR1shape[train$LotShape == "IR1"] <- 1
train$IR1shape[train$LotShape != "IR1"] <- 0
train$IR2shape[train$LotShape == "IR2"] <- 1
train$IR2shape[train$LotShape != "IR2"] <- 0
train$IR3shape[train$LotShape == "IR3"] <- 1
train$IR3shape[train$LotShape != "IR3"] <- 0

table(train$regshape)
table(train$IR1shape)
table(train$IR2shape)
table (train$IR3shape)
table(train$LandContour)
```

In order to save space, I'll just go through the rest of the categoricals using the provided codebook and pick up narrating again when it's done.

***

Cue muzak. Go look at the code tab if you want to read all of this. It's about 300 lines. Have a good time.

***

###Poking Around

```{r formatting_contour, echo=FALSE}
train$flat[train$LandContour == "Lvl"] <- 1
train$flat[train$LandContour != "Lvl"] <- 0

train$pubutil[train$Utilities == "AllPub"] <- 1
train$pubutil[train$Utilities != "AllPub"] <- 0

train$gentle_slope[train$LandSlope == "Gtl"] <- 1
train$gentle_slope[train$LandSlope != "Gtl"] <- 0

```



```{r groupmeans_lotconfig, echo=FALSE}
# summarize(group_by(train, LotConfig),
#           mean(SalePrice, na.rm=T))

train$culdesac_fr3[train$LotConfig %in% c("CulDSac", "FR3")] <- 1
train$culdesac_fr3[!train$LotConfig %in% c("CulDSac", "FR3")] <- 0

```



```{r groupmeans_nbhd, echo=FALSE}
nbhdprice <- summarize(group_by(train, Neighborhood),
          mean(SalePrice, na.rm=T))

#nbhdprice[order(nbhdprice$`mean(SalePrice, na.rm = T)`),]

nbhdprice_lo <- filter(nbhdprice, nbhdprice$`mean(SalePrice, na.rm = T)` < 140000)
nbhdprice_med <- filter(nbhdprice, nbhdprice$`mean(SalePrice, na.rm = T)` < 200000 &
                          nbhdprice$`mean(SalePrice, na.rm = T)` >= 140000 )
nbhdprice_hi <- filter(nbhdprice, nbhdprice$`mean(SalePrice, na.rm = T)` >= 200000)



train$nbhd_price_level[train$Neighborhood %in% nbhdprice_lo$Neighborhood] <- 1
train$nbhd_price_level[train$Neighborhood %in% nbhdprice_med$Neighborhood] <- 2
train$nbhd_price_level[train$Neighborhood %in% nbhdprice_hi$Neighborhood] <- 3

# summarize(group_by(train, Condition1),
#           mean(SalePrice, na.rm=T))

train$pos_features_1[train$Condition1 %in% c("PosA", "PosN")] <- 1
train$pos_features_1[!train$Condition1 %in% c("PosA", "PosN")] <- 0

# summarize(group_by(train, Condition2),
#           mean(SalePrice, na.rm=T))

train$pos_features_2[train$Condition2 %in% c("PosA", "PosN")] <- 1
train$pos_features_2[!train$Condition2 %in% c("PosA", "PosN")] <- 0

```

```{r groupmeans_bldg, echo=FALSE}
# summarize(group_by(train, BldgType),
#           mean(SalePrice, na.rm=T))

train$twnhs_end_or_1fam[train$BldgType %in% c("1Fam", "TwnhsE")] <- 1
train$twnhs_end_or_1fam[!train$BldgType %in% c("1Fam", "TwnhsE")] <- 0

housestyle_price <- summarize(group_by(train, HouseStyle),
          mean(SalePrice, na.rm=T))

housestyle_lo <- filter(housestyle_price, housestyle_price$`mean(SalePrice, na.rm = T)` < 140000)
housestyle_med <- filter(housestyle_price, housestyle_price$`mean(SalePrice, na.rm = T)` < 200000 &
                          housestyle_price$`mean(SalePrice, na.rm = T)` >= 140000 )
housestyle_hi <- filter(housestyle_price, housestyle_price$`mean(SalePrice, na.rm = T)` >= 200000)

train$house_style_level[train$HouseStyle %in% housestyle_lo$HouseStyle] <- 1
train$house_style_level[train$HouseStyle %in% housestyle_med$HouseStyle] <- 2
train$house_style_level[train$HouseStyle %in% housestyle_hi$HouseStyle] <- 3


roofstyle_price <- summarize(group_by(train, RoofStyle),
          mean(SalePrice, na.rm=T))

train$roof_hip_shed[train$RoofStyle %in% c("Hip", "Shed")] <- 1
train$roof_hip_shed[!train$RoofStyle %in% c("Hip", "Shed")] <- 0

roofmatl_price <- summarize(group_by(train, RoofMatl),
          mean(SalePrice, na.rm=T))

train$roof_matl_hi[train$RoofMatl %in% c("Membran", "WdShake", "WdShngl")] <- 1
train$roof_matl_hi[!train$RoofMatl %in% c("Membran", "WdShake", "WdShngl")] <- 0


price <- summarize(group_by(train, Exterior1st),
          mean(SalePrice, na.rm=T))

matl_lo_1 <- filter(price, price$`mean(SalePrice, na.rm = T)` < 140000)
matl_med_1<- filter(price, price$`mean(SalePrice, na.rm = T)` < 200000 &
                          price$`mean(SalePrice, na.rm = T)` >= 140000 )
matl_hi_1 <- filter(price, price$`mean(SalePrice, na.rm = T)` >= 200000)

train$exterior_1[train$Exterior1st %in% matl_lo_1$Exterior1st] <- 1
train$exterior_1[train$Exterior1st %in% matl_med_1$Exterior1st] <- 2
train$exterior_1[train$Exterior1st %in% matl_hi_1$Exterior1st] <- 3


price <- summarize(group_by(train, Exterior2nd),
          mean(SalePrice, na.rm=T))

matl_lo <- filter(price, price$`mean(SalePrice, na.rm = T)` < 140000)
matl_med <- filter(price, price$`mean(SalePrice, na.rm = T)` < 200000 &
                          price$`mean(SalePrice, na.rm = T)` >= 140000 )
matl_hi <- filter(price, price$`mean(SalePrice, na.rm = T)` >= 200000)

train$exterior_2[train$Exterior2nd %in% matl_lo$Exterior2nd] <- 1
train$exterior_2[train$Exterior2nd %in% matl_med$Exterior2nd] <- 2
train$exterior_2[train$Exterior2nd %in% matl_hi$Exterior2nd] <- 3

price <- summarize(group_by(train, MasVnrType),
          mean(SalePrice, na.rm=T))

train$exterior_mason_1[train$MasVnrType %in% c("Stone", "BrkFace") | is.na(train$MasVnrType)] <- 1
train$exterior_mason_1[!train$MasVnrType %in% c("Stone", "BrkFace") & !is.na(train$MasVnrType)] <- 0


price <- summarize(group_by(train, ExterQual),
          mean(SalePrice, na.rm=T))

train$exterior_cond[train$ExterQual == "Ex"] <- 4
train$exterior_cond[train$ExterQual == "Gd"] <- 3
train$exterior_cond[train$ExterQual == "TA"] <- 2
train$exterior_cond[train$ExterQual == "Fa"] <- 1


price <- summarize(group_by(train, ExterCond),
          mean(SalePrice, na.rm=T))

train$exterior_cond2[train$ExterCond == "Ex"] <- 5
train$exterior_cond2[train$ExterCond == "Gd"] <- 4
train$exterior_cond2[train$ExterCond == "TA"] <- 3
train$exterior_cond2[train$ExterCond == "Fa"] <- 2
train$exterior_cond2[train$ExterCond == "Po"] <- 1

```

```{r groupmeans_base, echo=FALSE}

price <- summarize(group_by(train, Foundation),
          mean(SalePrice, na.rm=T))

train$found_concrete[train$Foundation == "PConc"] <- 1
train$found_concrete[train$Foundation != "PConc"] <- 0  

price <- summarize(group_by(train, BsmtQual),
          mean(SalePrice, na.rm=T))

train$bsmt_cond1[train$BsmtQual == "Ex"] <- 5
train$bsmt_cond1[train$BsmtQual == "Gd"] <- 4
train$bsmt_cond1[train$BsmtQual == "TA"] <- 3
train$bsmt_cond1[train$BsmtQual == "Fa"] <- 2
train$bsmt_cond1[is.na(train$BsmtQual)] <- 1


price <- summarize(group_by(train, BsmtCond),
          mean(SalePrice, na.rm=T))

train$bsmt_cond2[train$BsmtCond == "Gd"] <- 5
train$bsmt_cond2[train$BsmtCond == "TA"] <- 4
train$bsmt_cond2[train$BsmtCond == "Fa"] <- 3
train$bsmt_cond2[is.na(train$BsmtCond)] <- 2
train$bsmt_cond2[train$BsmtCond == "Po"] <- 1


price <- summarize(group_by(train, BsmtExposure),
          mean(SalePrice, na.rm=T))

train$bsmt_exp[train$BsmtExposure == "Gd"] <- 5
train$bsmt_exp[train$BsmtExposure == "Av"] <- 4
train$bsmt_exp[train$BsmtExposure == "Mn"] <- 3
train$bsmt_exp[train$BsmtExposure == "No"] <- 2
train$bsmt_exp[is.na(train$BsmtExposure)] <- 1


price <- summarize(group_by(train, BsmtFinType1),
          mean(SalePrice, na.rm=T))

train$bsmt_fin1[train$BsmtFinType1 == "GLQ"] <- 5
train$bsmt_fin1[train$BsmtFinType1 == "Unf"] <- 4
train$bsmt_fin1[train$BsmtFinType1 == "ALQ"] <- 3
train$bsmt_fin1[train$BsmtFinType1 %in% c("BLQ", "Rec", "LwQ")] <- 2
train$bsmt_fin1[is.na(train$BsmtFinType1)] <- 1



price <- summarize(group_by(train, BsmtFinType2),
          mean(SalePrice, na.rm=T))

train$bsmt_fin2[train$BsmtFinType2 == "ALQ"] <- 6
train$bsmt_fin2[train$BsmtFinType2 == "Unf"] <- 5
train$bsmt_fin2[train$BsmtFinType2 == "GLQ"] <- 4
train$bsmt_fin2[train$BsmtFinType2 %in% c("Rec", "LwQ")] <- 3
train$bsmt_fin2[train$BsmtFinType2 == "BLQ"] <- 2
train$bsmt_fin2[is.na(train$BsmtFinType2)] <- 1

```

```{r hvac, echo=FALSE}

price <- summarize(group_by(train, Heating),
          mean(SalePrice, na.rm=T))

#table(train$Heating)

train$gasheat[train$Heating %in% c("GasA", "GasW")] <- 1
train$gasheat[!train$Heating %in% c("GasA", "GasW")] <- 0


price <- summarize(group_by(train, HeatingQC),
          mean(SalePrice, na.rm=T))

train$heatqual[train$HeatingQC == "Ex"] <- 5
train$heatqual[train$HeatingQC == "Gd"] <- 4
train$heatqual[train$HeatingQC == "TA"] <- 3
train$heatqual[train$HeatingQC == "Fa"] <- 2
train$heatqual[train$HeatingQC == "Po"] <- 1


price <- summarize(group_by(train, CentralAir),
          mean(SalePrice, na.rm=T))

train$air[train$CentralAir == "Y"] <- 1
train$air[train$CentralAir == "N"] <- 0


price <- summarize(group_by(train, Electrical),
          mean(SalePrice, na.rm=T))

train$standard_electric[train$Electrical == "SBrkr" | is.na(train$Electrical)] <- 1
train$standard_electric[!train$Electrical == "SBrkr" & !is.na(train$Electrical)] <- 0


price <- summarize(group_by(train, KitchenQual),
          mean(SalePrice, na.rm=T))

train$kitchen[train$KitchenQual == "Ex"] <- 4
train$kitchen[train$KitchenQual == "Gd"] <- 3
train$kitchen[train$KitchenQual == "TA"] <- 2
train$kitchen[train$KitchenQual == "Fa"] <- 1


price <- summarize(group_by(train, FireplaceQu),
          mean(SalePrice, na.rm=T))

train$fire[train$FireplaceQu == "Ex"] <- 5
train$fire[train$FireplaceQu == "Gd"] <- 4
train$fire[train$FireplaceQu == "TA"] <- 3
train$fire[train$FireplaceQu == "Fa"] <- 2
train$fire[train$FireplaceQu == "Po" | is.na(train$FireplaceQu)] <- 1

```

```{r cars, echo=FALSE}

#price <- summarize(group_by(train, GarageYrBlt),
          mean(SalePrice, na.rm=T))

#price <- summarize(group_by(train, LotFrontage),
          mean(SalePrice, na.rm=T))

price <- summarize(group_by(train, GarageType),
          mean(SalePrice, na.rm=T))

train$gar_attach[train$GarageType %in% c("Attchd", "BuiltIn")] <- 1
train$gar_attach[!train$GarageType %in% c("Attchd", "BuiltIn")] <- 0


price <- summarize(group_by(train, GarageFinish),
          mean(SalePrice, na.rm=T))

train$gar_finish[train$GarageFinish %in% c("Fin", "RFn")] <- 1
train$gar_finish[!train$GarageFinish %in% c("Fin", "RFn")] <- 0


price <- summarize(group_by(train, GarageQual),
          mean(SalePrice, na.rm=T))

train$garqual[train$GarageQual == "Ex"] <- 5
train$garqual[train$GarageQual == "Gd"] <- 4
train$garqual[train$GarageQual == "TA"] <- 3
train$garqual[train$GarageQual == "Fa"] <- 2
train$garqual[train$GarageQual == "Po" | is.na(train$GarageQual)] <- 1


price <- summarize(group_by(train, GarageCond),
          mean(SalePrice, na.rm=T))

train$garqual2[train$GarageCond == "Ex"] <- 5
train$garqual2[train$GarageCond == "Gd"] <- 4
train$garqual2[train$GarageCond == "TA"] <- 3
train$garqual2[train$GarageCond == "Fa"] <- 2
train$garqual2[train$GarageCond == "Po" | is.na(train$GarageCond)] <- 1


price <- summarize(group_by(train, PavedDrive),
          mean(SalePrice, na.rm=T))

train$paved_drive[train$PavedDrive == "Y"] <- 1
train$paved_drive[!train$PavedDrive != "Y"] <- 0
train$paved_drive[is.na(train$paved_drive)] <- 0

```

```{r misc, echo=FALSE}
price <- summarize(group_by(train, Functional),
          mean(SalePrice, na.rm=T))

train$housefunction[train$Functional %in% c("Typ", "Mod")] <- 1
train$housefunction[!train$Functional %in% c("Typ", "Mod")] <- 0


price <- summarize(group_by(train, PoolQC),
          mean(SalePrice, na.rm=T))

train$pool_good[train$PoolQC %in% c("Ex")] <- 1
train$pool_good[!train$PoolQC %in% c("Ex")] <- 0


price <- summarize(group_by(train, Fence),
          mean(SalePrice, na.rm=T))

train$priv_fence[train$Fence %in% c("GdPrv")] <- 1
train$priv_fence[!train$Fence %in% c("GdPrv")] <- 0


price <- summarize(group_by(train, MiscFeature),
          mean(SalePrice, na.rm=T))
#This doesn't seem worth using at the moment. May adjust later.


price <- summarize(group_by(train, SaleType),
          mean(SalePrice, na.rm=T))

# price[order(price$`mean(SalePrice, na.rm = T)`),]

train$sale_cat[train$SaleType %in% c("New", "Con")] <- 5
train$sale_cat[train$SaleType %in% c("CWD", "ConLI")] <- 4
train$sale_cat[train$SaleType %in% c("WD")] <- 3
train$sale_cat[train$SaleType %in% c("COD", "ConLw", "ConLD")] <- 2
train$sale_cat[train$SaleType %in% c("Oth")] <- 1


price <- summarize(group_by(train, SaleCondition),
          mean(SalePrice, na.rm=T))

# price[order(price$`mean(SalePrice, na.rm = T)`),]

train$sale_cond[train$SaleCondition %in% c("Partial")] <- 4
train$sale_cond[train$SaleCondition %in% c("Normal", "Alloca")] <- 3
train$sale_cond[train$SaleCondition %in% c("Family","Abnorml")] <- 2
train$sale_cond[train$SaleCondition %in% c("AdjLand")] <- 1


price <- summarize(group_by(train, MSZoning),
          mean(SalePrice, na.rm=T))

# price[order(price$`mean(SalePrice, na.rm = T)`),]

train$zone[train$MSZoning %in% c("FV")] <- 4
train$zone[train$MSZoning %in% c("RL")] <- 3
train$zone[train$MSZoning %in% c("RH","RM")] <- 2
train$zone[train$MSZoning %in% c("C (all)")] <- 1


price <- summarize(group_by(train, Alley),
          mean(SalePrice, na.rm=T))

# price[order(price$`mean(SalePrice, na.rm = T)`),]

train$alleypave[train$Alley %in% c("Pave")] <- 1
train$alleypave[!train$Alley %in% c("Pave")] <- 0


```

Done. Now, time to drop off the variables that have been made numeric and are no longer needed.
```{r drop_old_vars, echo=FALSE}

train$Street <- NULL
train$LotShape <- NULL
train$LandContour <- NULL
train$Utilities <- NULL
train$LotConfig <- NULL
train$LandSlope <- NULL
train$Neighborhood <- NULL
train$Condition1 <- NULL
train$Condition2 <- NULL
train$BldgType <- NULL
train$HouseStyle <- NULL
train$RoofStyle <- NULL
train$RoofMatl <- NULL

train$Exterior1st <- NULL
train$Exterior2nd <- NULL
train$MasVnrType <- NULL
train$ExterQual <- NULL
train$ExterCond <- NULL

train$Foundation <- NULL
train$BsmtQual <- NULL
train$BsmtCond <- NULL
train$BsmtExposure <- NULL
train$BsmtFinType1 <- NULL
train$BsmtFinType2 <- NULL

train$Heating <- NULL
train$HeatingQC <- NULL
train$CentralAir <- NULL
train$Electrical <- NULL
train$KitchenQual <- NULL
train$FireplaceQu <- NULL

train$GarageType <- NULL
train$GarageFinish <- NULL
train$GarageQual <- NULL
train$GarageCond <- NULL
train$PavedDrive <- NULL

train$Functional <- NULL
train$PoolQC <- NULL
train$Fence <- NULL
train$MiscFeature <- NULL
train$SaleType <- NULL
train$SaleCondition <- NULL
train$MSZoning <- NULL
train$Alley <- NULL

```


Another thing I want to do is build some interactions that may be worth looking at. 
For example, if the house has a pool, is it more important that it has a big deck, or something like that? 
I used correlation visuals like this to do it- you can choose what you'd want to put in and how many variations
you want to make.

```{r correlations, results="asis"}
library(corrplot)


correlations <- cor(train[,c(5,6,7,8, 16:25)], use="everything")
corrplot(correlations, method="circle", type="lower",  sig.level = 0.01, insig = "blank")

correlations <- cor(train[,c(5,6,7,8, 26:35)], use="everything")
corrplot(correlations, method="circle", type="lower",  sig.level = 0.01, insig = "blank")

correlations <- cor(train[,c(5,6,7,8, 66:75)], use="everything")
corrplot(correlations, method="circle", type="lower",  sig.level = 0.01, insig = "blank")
```

```{r}
colSums(is.na(train))  
# Find out are there missing values that are causing some "?" type outputs in correlations
```

The reason GarageYrBlt is "?" is because there are missing values in this variables.  
Use 'pairwise.complete.obs' option to get correlation even if different rows 
have different missing values 

However, regression requires no missing values in any row.

Anyway, the correlations that both have to do with square footage I am going to discount, because size of the total and size of a floor, for example, are obvious correlations. 

This is fun too- I picked a few of the variables that had a lot of correlation strengths. Basements have for (i in 1:ncol(vars)) {
been getting bigger over time, apparently. As have the sizes of the living areas. Good to know!


I'm also interested in the relationship between sale price and some numeric variables, but these can be tougher to visualize.


```{r scatter_num, message=FALSE}
library(car)

scatterplot(SalePrice ~ YearBuilt, data=train,  xlab="Year Built", ylab="Sale Price", grid=FALSE)
scatterplot(SalePrice ~ YrSold, data=train,  xlab="Year Sold", ylab="Sale Price", grid=FALSE)
scatterplot(SalePrice ~ X1stFlrSF, data=train,  xlab="Square Footage Floor 1", ylab="Sale Price", grid=FALSE)

```

Prices are higher for new houses, that makes sense. Also, we can see that sale prices dropped when we would expect (thanks, housing crisis).
We also have some outliers on first floor square footage- probably bad data but it's not going to have a huge influence - !!!!

EXERCISE: REMOVE THIS worst outlier(influential obs and redo the analysis and see how it changes the model parameter estimates)

Let us do more of this!!

```{r}
#sapply(1:3, function(x, y) mean(y[,x]), y=m)

names(train)
```


```{r interactions}
#Fix some NAs
train$GarageYrBlt[is.na(train$GarageYrBlt)] <- 0
train$MasVnrArea[is.na(train$MasVnrArea)] <- 0
train$LotFrontage[is.na(train$LotFrontage)] <- 0

#Interactions based on correlation
train$year_qual <- train$YearBuilt*train$OverallQual #overall condition
train$year_r_qual <- train$YearRemodAdd*train$OverallQual #quality x remodel
train$qual_bsmt <- train$OverallQual*train$TotalBsmtSF #quality x basement size

train$livarea_qual <- train$OverallQual*train$GrLivArea #quality x living area
train$qual_bath <- train$OverallQual*train$FullBath #quality x baths

train$qual_ext <- train$OverallQual*train$exterior_cond #quality x exterior

names(train)

```

***


###Model Prepping

Then, partition! I always like to use the caret partitioning function.

```{r partition}
library(caret)
outcome <- train$SalePrice

partition <- createDataPartition(y=outcome,
                                 p=.6,
                                 list=F)
training <- train[partition,]
testing <- train[-partition,]
```

***

###A Linear Model

Finally, we have our data and can build some models. Since our outcome is a continuous numeric variable, we want a linear model, not a GLM. First, let's just toss it all in there. I always like to use a proper regression model as my first examination of the data, to get a feel for what's there.

```{r lm}

lm_model <- lm(SalePrice ~ ., data=training)
summary(lm_model)
par(mfrow=c(2,2))
plot(lm_model)
```

Lots of stuff we can drop right off, that's good. Some multicollinearity is making the model drop a few variables, but that's ok.

Also, our R-squared is not too bad! In case you're unfamiliar, that indicates what percent of the variation in the outcome is explained using the model we designed.
```{r}

train1<-training[-c(1299),]
lm_model_levout <- lm(SalePrice ~ ., data=train1)
summary(lm_model_levout)
```


## Note plot area has become a significant variable
## what are the other changes?

```

## NOtes on avPlot


```{r influentialobs}
plot(lm_model_levout)
```

```{r}
names(train1)
```

```{r lm2}

lm_model_18_levout <- lm(SalePrice ~     OverallCond+MasVnrArea+BsmtFinSF1+BsmtFinSF2+BsmtUnfSF+GarageCars+regshape+IR1shape
+IR2shape+nbhd_price_level+pos_features_2+roof_matl_hi+exterior_cond+pool_good+qual_ext, data=train1)
summary(lm_model_18_levout)

```

That's our model with the important stuff, more or less. How does the RMSE turn out? That is our outcome of interest, after all.


```{r testing}

prediction <- predict(lm_model_18_levout, testing, type="response")
model_output <- cbind(testing, prediction)

model_output$log_prediction <- log(model_output$prediction)
model_output$log_SalePrice <- log(model_output$SalePrice)

#Test with RMSE

rmse(model_output$log_SalePrice,model_output$log_prediction)

```

```{r testing}

prediction <- predict(lm_model, testing, type="response")
model_output <- cbind(testing, prediction)

model_output$log_prediction <- log(model_output$prediction)
model_output$log_SalePrice <- log(model_output$SalePrice)

#Test with RMSE

rmse(model_output$log_SalePrice,model_output$log_prediction)

```



#######################################################
###A Random Forest

Not too bad, given that this is just an LM. Let's try training the model with an RF. Let's use all the variables and see how things look, since randomforest does its own feature selection.

```{r caret1}

model_1 <- randomForest(SalePrice ~ ., data=training)


# Predict using the test set
prediction <- predict(model_1, testing)
model_output <- cbind(testing, prediction)


model_output$log_prediction <- log(model_output$prediction)
model_output$log_SalePrice <- log(model_output$SalePrice)

#Test with RMSE

rmse(model_output$log_SalePrice,model_output$log_prediction)


```